The pollination trade-off

### 2018-02-27 publication/manuscript.Rmd
Add questions and observations to manuscript

>>>>

## Questions & Observations

* Is there a better way to obtain a plant metric of temporal overlap? --- *Will use decomposition and distance metrics for this instead of the Pianka method*
* Results shown here use `r n_distinct(readd(glanced_random)$model)` bootstrap replicates. Will scale up to 1000 models once methods are nailed down. 
* Should I include the analysis of global models at all?
